Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-10 ms.tex
mispellings galore

\author[Generozov, Stone, \& Metzger]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
  Columbia Astrophysics Labratory, Columbia University, 550 West 120th
  Street, New York, NY 10027}

@@

Understanding why most SMBHs appear to be inactive requires
characterizing their gaseous environments.  Gas near the sphere of
influence of the SMBH, hereafter the `circumnuclear medium' (CNM),
controls the mass accretion rate, $\dot{M}$.  The accretion rate in
turn sets the luminosity of the black hole and the impact of this
energy and momentum output on larger physical scales (`feedback').
The presence of dense gas in the nucleus may also lead to runaway
cooling, resulting in bursty episodes of star formation and AGN
activity (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}).

>>>>

\author[Generozov, Stone, \& Metzger]{Aleksey Generozov$\thanks{E-mail: ag@astro.columbia.edu}$, Nicholas Stone, Brian~D.~Metzger\\
  Columbia Astrophysics Laboratory, Columbia University, 550 West 120th
  Street, New York, NY 10027}

@@

Understanding why most SMBHs appear to be inactive requires
characterizing their gaseous environments.  Gas near the sphere of
influence of the SMBH, hereafter the `circumnuclear medium' (CNM),
controls the mass accretion rate, $\dot{M}$.  The accretion rate in
turn sets the luminosity of the black hole and the impact of this
energy and momentum output on larger physical scales (`feedback').
The presence of dense gas in the nuclear region may also lead to runaway
cooling, resulting in bursty episodes of star formation and AGN
activity (e.g.~\citealt{Ciotti&Ostriker07}; \citealt{Ciotti+10}).
